---
title: "Evolution-Multiple-Stressors: Supplementary Materials"
author: "James Orr"
output:
   html_notebook:
     code_folding: hide
     theme: flatly
     toc: true
     toc_depth: 4
     number_sections: no
---

```{r, echo=FALSE, results='hide'}
rm(list = ls())           # clear the environment 

# Packages
library(tidyverse)        # Organising and manipulating data
library(gsubfn)           # To use list[]
library(plotrix)          # To use enhance list[] functionality
library(latex2exp)        # To use Tex in figures

# Packages to make the Gif
library(plot3Drgl)        # For interactive 3D plots - XQuartz required (macs)
library(magick)           # For exporting gifs 
```


### Intro

This R notebook contains the code used to create the supplementary figures and videos for the paper: *Rapid Evolution Generates Synergism Between Multiple Stressors and Complicates Ecological Restoration*. 

We use data and dataframes generated in the `Rotifer-Stressor-Analysis` notebook. 

<br>

- **Import data and organise**

```{r, echo=TRUE, results='hide'}
rot_pop <- read.csv("Data/Outputs/population_growth.csv", header = TRUE, 
                     stringsAsFactors=FALSE)

rot_pop <- rot_pop %>%
  mutate(label = case_when(
    evolline == 1 ~ "Con",
    evolline == 2 ~ "S",
    evolline == 3 ~ "C",
    evolline == 4 ~ "T",
    evolline == 5 ~ "SC",
    evolline == 6 ~ "ST",
    evolline == 7 ~ "CT",
    evolline == 8 ~ "SCT"))

growth_trend_data <- read.csv("Data/Outputs/stressor_interactions.csv", 
                                  header = TRUE, stringsAsFactors = FALSE)
growth_trend_data$treatment_F <- as.factor(growth_trend_data$treatment_F)


## Colour scheme ## 
j.red <- rgb(245/255, 159/255, 148/255)
j.blue <- rgb(195/255, 214/255, 245/255)
j.red_alpha <- rgb(245/255, 159/255, 148/255, alpha = 0.65)
j.blue_alpha <- rgb(195/255, 214/255, 245/255, alpha = 0.65)
```

- **Make logical subsets**

```{r, echo=TRUE}
###### Evolved Population Growth Rates #######
Na_in_Na <- subset(rot_pop, treat_num == "10")
Cu_in_Cu <- subset(rot_pop, treat_num == "19")
Temp_in_Temp <- subset(rot_pop, treat_num == "28")
NaCu_in_NaCu <- subset(rot_pop, treat_num == "37")
NaTemp_in_NaTemp <- subset(rot_pop, treat_num == "46")
CuTemp_in_CuTemp <- subset(rot_pop, treat_num == "55")
All_in_All <- subset(rot_pop, treat_num == "64")

####### Non-Evolved Population Growth Rate ########
Control_in_Control <- subset(rot_pop, treat_num == "1")
Control_in_Na <- subset(rot_pop, treat_num == "2")
Control_in_Cu <- subset(rot_pop, treat_num == "3")
Control_in_Temp <- subset(rot_pop, treat_num == "4")
Control_in_NaCu <- subset(rot_pop, treat_num == "5")
Control_in_NaTemp <- subset(rot_pop, treat_num == "6")
Control_in_CuTemp <- subset(rot_pop, treat_num == "7")
Control_in_All <- subset(rot_pop, treat_num == "8")

#### For Performance Space Plots ####
NaCu_in_Na <- subset(rot_pop, treat_num == "34")
NaCu_in_Cu <- subset(rot_pop, treat_num == "35")
NaCu_in_Temp <- subset(rot_pop, treat_num == "36")
NaTemp_in_Na <- subset(rot_pop, treat_num == "42")
NaTemp_in_Cu <- subset(rot_pop, treat_num == "43")
NaTemp_in_Temp <- subset(rot_pop, treat_num == "44")
CuTemp_in_Na <- subset(rot_pop, treat_num == "50")
CuTemp_in_Cu <- subset(rot_pop, treat_num == "51")
CuTemp_in_Temp <- subset(rot_pop, treat_num == "52")
All_in_Na <- subset(rot_pop, treat_num == "58")
All_in_Cu <- subset(rot_pop, treat_num == "59")
All_in_Temp <- subset(rot_pop, treat_num == "60")
Na_in_Cu <- subset(rot_pop, treat_num == "11")
Cu_in_Na <- subset(rot_pop, treat_num == "18")
Na_in_Temp <- subset(rot_pop, treat_num == "12")
Temp_in_Na <- subset(rot_pop, treat_num == "26")
Cu_in_Temp <- subset(rot_pop, treat_num == "20")
Temp_in_Cu <- subset(rot_pop, treat_num == "27")

#### For Removal of Stressors #####
Na_in_Control <- subset(rot_pop, treat_num == "9")
Cu_in_Control <- subset(rot_pop, treat_num == "17")
Temp_in_Control <- subset(rot_pop, treat_num == "25")
NaCu_in_Control <- subset(rot_pop, treat_num == "33")
NaTemp_in_Control <- subset(rot_pop, treat_num == "41")
CuTemp_in_Control <- subset(rot_pop, treat_num == "49")
All_in_Control <- subset(rot_pop, treat_num == "57")
All_in_NaCu <- subset(rot_pop, treat_num == "61")
All_in_NaTemp <- subset(rot_pop, treat_num == "62")
All_in_CuTemp <- subset(rot_pop, treat_num == "63")
```

- **Calculate required summary statistics**

```{r, echo=TRUE}
## Some functions to speed things up ##

std.error <- function(x){ 
  return( sqrt( var(x) / length(x) ) ) 
  }

statistics <- function(x, Con){
  n <- length(x)
  m <- mean(x)
  se <- std.error(x)
  sd <- sd(x)
  mcon <- mean(Con)
  sdcon <- sd(Con)
  ncon <- length(Con)
  raw_e <- mcon - m
  raw_v <- (sdcon^2 / ncon) + (sd^2 / n)
  raw_se <- sqrt(raw_v)
  return(c(m, se, raw_e, raw_se))
  }

######################## Evolved ########################

list[mgrowth_Na_in_Na, segrowth_Na_in_Na, rawD_na_on_e, rawSE_na_on_e] <- 
  statistics(Na_in_Na$mean_growth, Control_in_Control$mean_growth)

list[mgrowth_Cu_in_Cu, segrowth_Cu_in_Cu, rawD_cu_on_e, rawSE_cu_on_e] <- 
  statistics(Cu_in_Cu$mean_growth, Control_in_Control$mean_growth)

list[mgrowth_Temp_in_Temp, segrowth_Temp_in_Temp, rawD_temp_on_e, 
     rawSE_temp_on_e] <- 
  statistics(Temp_in_Temp$mean_growth, Control_in_Control$mean_growth)

list[mgrowth_NaCu_in_NaCu, segrowth_NaCu_in_NaCu, rawD_nacu_on_e, 
     rawSE_nacu_on_e] <- 
  statistics(NaCu_in_NaCu$mean_growth, Control_in_Control$mean_growth)

list[mgrowth_NaTemp_in_NaTemp, segrowth_NaTemp_in_NaTemp, rawD_natemp_on_e, 
     rawSE_natemp_on_e] <- 
  statistics(NaTemp_in_NaTemp$mean_growth, Control_in_Control$mean_growth)

list[mgrowth_CuTemp_in_CuTemp, segrowth_CuTemp_in_CuTemp, rawD_cutemp_on_e, 
     rawSE_cutemp_on_e] <- 
  statistics(CuTemp_in_CuTemp$mean_growth, Control_in_Control$mean_growth)

list[mgrowth_All_in_All, segrowth_All_in_All, rawD_all_on_e, rawSE_all_on_e] <- 
  statistics(All_in_All$mean_growth, Control_in_Control$mean_growth)


######################## Control ########################

mgrowth_Control_in_Control <- mean(Control_in_Control$mean_growth)
segrowth_Control_in_Control <- std.error(Control_in_Control$mean_growth)

list[mgrowth_Control_in_Na, segrowth_Control_in_Na, rawD_na_on_c, 
     rawSE_na_on_c] <- 
  statistics(Control_in_Na$mean_growth, Control_in_Control$mean_growth)

list[mgrowth_Control_in_Cu, segrowth_Control_in_Cu, rawD_cu_on_c, 
     rawSE_cu_on_c] <- 
  statistics(Control_in_Cu$mean_growth, Control_in_Control$mean_growth)

list[mgrowth_Control_in_Temp, segrowth_Control_in_Temp, rawD_temp_on_c, 
     rawSE_temp_on_c] <- 
  statistics(Control_in_Temp$mean_growth, Control_in_Control$mean_growth)

list[mgrowth_Control_in_NaCu, segrowth_Control_in_NaCu, rawD_nacu_on_c, 
     rawSE_nacu_on_c] <- 
  statistics(Control_in_NaCu$mean_growth, Control_in_Control$mean_growth)

list[mgrowth_Control_in_NaTemp, segrowth_Control_in_NaTemp, rawD_natemp_on_c, 
     rawSE_natemp_on_c] <- 
  statistics(Control_in_NaTemp$mean_growth, Control_in_Control$mean_growth)

list[mgrowth_Control_in_CuTemp, segrowth_Control_in_CuTemp, rawD_cutemp_on_c, 
     rawSE_cutemp_on_c] <- 
  statistics(Control_in_CuTemp$mean_growth, Control_in_Control$mean_growth)

list[mgrowth_Control_in_All, segrowth_Control_in_All, rawD_all_on_c, 
     rawSE_all_on_c] <- 
  statistics(Control_in_All$mean_growth, Control_in_Control$mean_growth)
```

- **Calculate distances and coordinates** 

```{r, echo=TRUE}
coord <- function(x){
  return(x/2)
}

###### Realised #######
coord_nacu_con <- coord(rawD_nacu_on_c)
coord_natemp_con <- coord(rawD_natemp_on_c)
coord_cutemp_con <- coord(rawD_cutemp_on_c)
coord_all_con <- coord(rawD_all_on_c)
coord_nacu_evo <- coord(rawD_nacu_on_e)
coord_natemp_evo <- coord(rawD_natemp_on_e)
coord_cutemp_evo <- coord(rawD_cutemp_on_e)
coord_all_evo<- coord(rawD_all_on_e)
###### Additive #######
coord_nacu_add_con <- coord(rawD_na_on_c+rawD_cu_on_c)
coord_natemp_add_con <- coord(rawD_na_on_c+rawD_temp_on_c)
coord_cutemp_add_con <- coord(rawD_cu_on_c+rawD_temp_on_c)
coord_all_add_con <- coord(rawD_na_on_c+rawD_cu_on_c+rawD_temp_on_c)
coord_nacu_add_evo <- coord(rawD_na_on_e+(rawD_cu_on_e))
coord_natemp_add_evo <- coord(rawD_na_on_e+rawD_temp_on_e)
coord_cutemp_add_evo <- coord(rawD_temp_on_e+(rawD_cu_on_e))
coord_all_add_evo<- coord(rawD_na_on_e+rawD_temp_on_e+(rawD_cu_on_e))
###### Error Bars ######
plus_nacu_con <- coord(rawD_nacu_on_c+rawSE_nacu_on_c)
plus_natemp_con <- coord(rawD_natemp_on_c+rawSE_natemp_on_c)
plus_cutemp_con <- coord(rawD_cutemp_on_c+rawSE_cutemp_on_c)
plus_nacu_evo <- coord(rawD_nacu_on_e+rawSE_nacu_on_e)
plus_natemp_evo <- coord(rawD_natemp_on_e+rawSE_natemp_on_e)
plus_cutemp_evo <- coord(rawD_cutemp_on_e+rawSE_cutemp_on_e)
min_nacu_con <- coord(rawD_nacu_on_c-rawSE_nacu_on_c)
min_natemp_con <- coord(rawD_natemp_on_c-rawSE_natemp_on_c)
min_cutemp_con <- coord(rawD_cutemp_on_c-rawSE_cutemp_on_c)
min_nacu_evo <- coord(rawD_nacu_on_e-rawSE_nacu_on_e)
min_natemp_evo <- coord(rawD_natemp_on_e-rawSE_natemp_on_e)
min_cutemp_evo <- coord(rawD_cutemp_on_e-rawSE_cutemp_on_e)

###### population coords ########
coord_nacu_con_pop <- coord(mgrowth_Control_in_Control-
                                   Control_in_NaCu$mean_growth)
coord_natemp_con_pop <-coord(mgrowth_Control_in_Control-
                                    Control_in_NaTemp$mean_growth)
coord_cutemp_con_pop <-coord(mgrowth_Control_in_Control-
                                    Control_in_CuTemp$mean_growth)
coord_all_con_pop <- coord(mgrowth_Control_in_Control-
                                  Control_in_All$mean_growth)
coord_nacu_evo_pop <- coord(mgrowth_Control_in_Control-
                                   NaCu_in_NaCu$mean_growth)
coord_natemp_evo_pop <- coord(mgrowth_Control_in_Control-
                                     NaTemp_in_NaTemp$mean_growth)
coord_cutemp_evo_pop <- coord(mgrowth_Control_in_Control-
                                     CuTemp_in_CuTemp$mean_growth)
coord_all_evo_pop <- coord(mgrowth_Control_in_Control-
                                  All_in_All$mean_growth)

#### additive expectation for 3D video #####
coord_all_con_add <- coord(rawD_na_on_c+rawD_cu_on_c+rawD_temp_on_c)
coord_all_evo_add <- coord(rawD_na_on_e+rawD_cu_on_e+rawD_temp_on_e)
```

- **means of populations**

```{r, echo=TRUE}
### gathering mean data points 
mgrowth_NaCu_in_Na <- mean(NaCu_in_Na$mean_growth)
mgrowth_NaCu_in_Cu <- mean(NaCu_in_Cu$mean_growth)
mgrowth_NaTemp_in_Na <- mean(NaTemp_in_Na$mean_growth)
mgrowth_NaTemp_in_Temp <- mean(NaTemp_in_Temp$mean_growth)
mgrowth_CuTemp_in_Cu <- mean(CuTemp_in_Cu$mean_growth)
mgrowth_CuTemp_in_Temp <- mean(CuTemp_in_Temp$mean_growth)
mgrowth_All_in_Na <- mean(All_in_Na$mean_growth)
mgrowth_All_in_Cu <- mean(All_in_Cu$mean_growth)
mgrowth_All_in_Temp <- mean(All_in_Temp$mean_growth)
mgrowth_Na_in_Control <- mean(Na_in_Control$mean_growth)
mgrowth_Cu_in_Control <- mean(Cu_in_Control$mean_growth)
mgrowth_Temp_in_Control <- mean(Temp_in_Control$mean_growth)
mgrowth_All_in_NaCu <- mean(All_in_NaCu$mean_growth)
mgrowth_All_in_NaTemp <- mean(All_in_NaTemp$mean_growth)
mgrowth_All_in_CuTemp <- mean(All_in_CuTemp$mean_growth)
mgrowth_NaCu_in_Control <- mean(NaCu_in_Control$mean_growth)
mgrowth_NaTemp_in_Control <- mean(NaTemp_in_Control$mean_growth)
mgrowth_CuTemp_in_Control <- mean(CuTemp_in_Control$mean_growth)
```


- **Calculate adaptations** 

```{r, echo=TRUE}
#### NA ####
ad_na_to_na <- Na_in_Na$mean_growth - mgrowth_Control_in_Na
ad_na_to_cu <- Na_in_Cu$mean_growth - mgrowth_Control_in_Cu
ad_na_to_temp <- Na_in_Temp$mean_growth - mgrowth_Control_in_Temp

#### CU ####
ad_cu_to_na <- Cu_in_Na$mean_growth - mgrowth_Control_in_Na
ad_cu_to_cu <- Cu_in_Cu$mean_growth - mgrowth_Control_in_Cu
ad_cu_to_temp <- Cu_in_Temp$mean_growth - mgrowth_Control_in_Temp 

#### TEMP ####
ad_temp_to_na <- Temp_in_Na$mean_growth - mgrowth_Control_in_Na
ad_temp_to_cu <- Temp_in_Cu$mean_growth - mgrowth_Control_in_Cu
ad_temp_to_temp <- Temp_in_Temp$mean_growth - mgrowth_Control_in_Temp 

#### NACU ####
ad_nacu_to_na <- NaCu_in_Na$mean_growth - mgrowth_Control_in_Na
ad_nacu_to_cu <- NaCu_in_Cu$mean_growth - mgrowth_Control_in_Cu
ad_nacu_to_temp <- NaCu_in_Temp$mean_growth - mgrowth_Control_in_Temp 

#### NATEMP ####
ad_natemp_to_na <- NaTemp_in_Na$mean_growth - mgrowth_Control_in_Na
ad_natemp_to_cu <- NaTemp_in_Cu$mean_growth - mgrowth_Control_in_Cu
ad_natemp_to_temp <- NaTemp_in_Temp$mean_growth - mgrowth_Control_in_Temp 

#### CUTEMP ####
ad_cutemp_to_na <- CuTemp_in_Na$mean_growth - mgrowth_Control_in_Na
ad_cutemp_to_cu <- CuTemp_in_Cu$mean_growth - mgrowth_Control_in_Cu
ad_cutemp_to_temp <- CuTemp_in_Temp$mean_growth - mgrowth_Control_in_Temp 

#### ALL ####
ad_all_to_na <- All_in_Na$mean_growth - mgrowth_Control_in_Na
ad_all_to_cu <- All_in_Cu$mean_growth - mgrowth_Control_in_Cu
ad_all_to_temp <- All_in_Temp$mean_growth - mgrowth_Control_in_Temp 
```

- **Calculate removal effect** 

```{r, echo=TRUE}
# See supplementary note for an explanation of why this step is required 
# The growth rate of NaCu in Cu contains the ad_nacu_to_cu 
# But it also contains the removal effect (i.e. maladaptation) of removing na 
# We don't have access to this information directly 
# So we make approximations based on the information we do have 

### Effect of removing a stressor
Na_removed <- mgrowth_Na_in_Control-mgrowth_Control_in_Control
Cu_removed <- mgrowth_Cu_in_Control-mgrowth_Control_in_Control
Temp_removed <- mgrowth_Temp_in_Control-mgrowth_Control_in_Control

### For the different evolved lines  
NaCu_Na_removed <- Na_removed
NaCu_Cu_removed <- Cu_removed
NaTemp_Na_removed <- Na_removed
NaTemp_Temp_removed <- Temp_removed
CuTemp_Cu_removed <- Cu_removed
CuTemp_Temp_removed <- Temp_removed

######### Special case of three stressors ###########
# Using information about double evolved lines in their own environment
# Explanation in supplementary note:  all_performance = 0.5*Adj*colvec
# all_performance is what we want (performance space coordinates)
# col_vec is what we know (adaptation of abc to ab/ac/bc) and removal of a/b/c
# Adj = adjoint matrix, details in supplementary note 

# Defining colvec
colvec_1 <- (mgrowth_All_in_NaCu-mgrowth_Control_in_NaCu)-Temp_removed
colvec_2 <- (mgrowth_All_in_NaTemp-mgrowth_Control_in_NaTemp)-Cu_removed
colvec_3 <- (mgrowth_All_in_CuTemp-mgrowth_Control_in_CuTemp)-Na_removed
colvec <- c(colvec_1, colvec_2, colvec_3)

# Definig Adj
Adj <- matrix(c(1, 1, -1, 1, -1, 1, -1, 1, 1), nrow=3)

# Calculating perfomrnace space coordinates
all_performance <- 0.5*Adj%*%colvec      #   %*% is matrix multiplication

# Calculate the removal effect (to be consistent with older code)
All_CuTemp_removed <- mean(ad_all_to_na)- all_performance[1]
All_NaTemp_removed <- mean(ad_all_to_cu) - all_performance[2]
All_NaCu_removed <- mean(ad_all_to_temp) - all_performance[3]

# Extra information required for 3d plots
NaCu_NaCu_removed <- Na_removed + Cu_removed
NaTemp_NaTemp_removed <- Na_removed + Temp_removed
CuTemp_CuTemp_removed <- Cu_removed + Temp_removed
```

<br>
<br>

### Suplementary Fig 1: Scenario 2

```{r, echo=FALSE, fig.width=6.5, fig.height=4.0, results='hide'}

# On my desktop monitor#
### fig.width = 6.5 ###
### fig.height = 4.0 ###

## Layout of plots ##
layout(matrix(c(1, 5,
                2, 5,
                3, 5,
                4, 5), 
              nrow=4, byrow=TRUE), widths = c(1, 1.61))


###### NaCu #######

par(mar=c(2, 6, 8, 2)) # bottom, left, top, right

NaCu.bar <- barplot(c(rawD_na_on_c, 
                     rawD_cu_on_c, 
                     rawD_nacu_on_c,
                     rawD_na_on_c+rawD_cu_on_c,
                     rawD_na_on_c, 
                     rawD_cu_on_c, 
                     rawD_nacu_on_e,
                     rawD_na_on_c+rawD_cu_on_c), 
                   las = 1, xlab = "", ylab = "", yaxt = "n",
                   names.arg = c("S", "C", "SC", "+",
                                 "S'", "C'", "SC'", "+'"), 
                   cex.names = 1.5, 
                   ylim = c(-0.05, 0.365),
                   col = c(j.blue,
                           j.blue,
                           j.blue,
                           rgb(0.9, 0.9, 0.9),
                           j.blue,
                           j.blue,
                           j.red,
                           rgb(0.9, 0.9, 0.9)),
                   border = "white",
                   space = c(0.5, 0.5, 0.5, 0.5, 
                             2.0, 0.5, 0.5, 0.5))

axis(side = 2, at = c(0.0, 0.15, 0.3), 
     labels = c("0%", "15%", "30%"),
     cex.axis=1.5, las=1, lwd=1, lwd.ticks = 1)

abline(h = 0, lty = 1, lwd = 1, col = rgb(0.35, 0.35, 0.35))

mufin <- c(rawD_na_on_c, 
           rawD_cu_on_c, 
           rawD_nacu_on_c,
           rawD_na_on_c+rawD_cu_on_c,
           rawD_na_on_c, 
           rawD_cu_on_c,
           rawD_nacu_on_e,
           rawD_na_on_c+rawD_cu_on_c)
sefin <- c(rawSE_na_on_c, 
           rawSE_cu_on_c,
           rawSE_nacu_on_c,
           0,
           rawSE_na_on_c, 
           rawSE_cu_on_c, 
           rawSE_nacu_on_e,
           0)
arrows( x0 = NaCu.bar, x1 = NaCu.bar, 
        y0 = mufin + sefin, y1 = mufin - sefin,
         code = 3, length = 0.05, angle = 90, lwd = 2,
        col = c(rgb(.4, .4, .4),
                rgb(.4, .4, .4),
                rgb(.4, .4, .4),
                rgb(1, 1, 1),
                rgb(.4, .4, .4),
                rgb(.4, .4, .4),
                rgb(.4, .4, .4),
                rgb(1, 1, 1)))

# Add points for populations 
points(x = c(0.25, 0.25, 0.25, 0.25),
       y = mgrowth_Control_in_Control-Control_in_Na$mean_growth,
       col = rgb(0, 0, 0, 0.05), bg = j.blue_alpha, pch = 21, cex = 1)
points(x = c(1.75, 1.75, 1.75, 1.75),
       y = mgrowth_Control_in_Control-Control_in_Cu$mean_growth,
       col = rgb(0, 0, 0, 0.05), bg = j.blue_alpha, pch = 21, cex = 1)
points(x = c(3.25, 3.25, 3.25, 3.25),
       y = mgrowth_Control_in_Control-Control_in_NaCu$mean_growth,
       col = rgb(0, 0, 0, 0.05), bg = j.blue_alpha, pch = 21, cex = 1)

points(x = c(7.75, 7.75, 7.75, 7.75),
       y = mgrowth_Control_in_Control-Control_in_Na$mean_growth,
       col = rgb(0, 0, 0, 0.05), bg = j.blue_alpha, pch = 21, cex = 1)
points(x = c(9.25, 9.25, 9.25, 9.25),
       y = mgrowth_Control_in_Control-Control_in_Cu$mean_growth,
       col = rgb(0, 0, 0, 0.05), bg = j.blue_alpha, pch = 21, cex = 1)
points(x = c(10.75, 10.75, 10.75),
       y = mgrowth_Control_in_Control-NaCu_in_NaCu$mean_growth,
       col = rgb(0, 0, 0, 0.05), bg = j.red_alpha, pch = 21, cex = 1)


####################### NaTemp####################### 

par(mar=c(4, 6, 6, 2)) # bottom, left, top, right

NaTemp.bar <- barplot(c(rawD_na_on_c, 
                     rawD_temp_on_c, 
                     rawD_natemp_on_c,
                     rawD_na_on_c+rawD_temp_on_c,
                     rawD_na_on_c, 
                     rawD_temp_on_c, 
                     rawD_natemp_on_e,
                     rawD_na_on_c+rawD_temp_on_c), 
                   las = 1, xlab = "", ylab = "", yaxt = "n",
                   names.arg = c("S", "T", "ST", "+",
                                 "S'", "T'", "ST'", "+'"), 
                   cex.names = 1.5, 
                   ylim = c(-0.05, 0.365),
                   col = c(j.blue,
                           j.blue,
                           j.blue,
                           rgb(0.9, 0.9, 0.9),
                           j.blue,
                           j.blue,
                           j.red,
                           rgb(0.9, 0.9, 0.9)),
                   border = "white",
                   space = c(0.5, 0.5, 0.5, 0.5, 
                             2.0, 0.5, 0.5, 0.5))

axis(side = 2, at = c(0.0, 0.15, 0.3), 
     labels = c("0%", "15%", "30%"),
     cex.axis=1.5, las=1, lwd=1, lwd.ticks = 1)

abline(h = 0, lty = 1, lwd = 1, col = rgb(0.35, 0.35, 0.35))

mufin <- c(rawD_na_on_c, 
           rawD_temp_on_c, 
           rawD_natemp_on_c,
           rawD_na_on_c+rawD_temp_on_c,
           rawD_na_on_c, 
           rawD_temp_on_c,
           rawD_natemp_on_e,
           rawD_na_on_c+rawD_temp_on_c)
sefin <- c(rawSE_na_on_c, 
           rawSE_temp_on_c,
           rawSE_natemp_on_c,
           0,
           rawSE_na_on_c, 
           rawSE_temp_on_c, 
           rawSE_natemp_on_e,
           0)
arrows( x0 = NaTemp.bar, x1 = NaTemp.bar, 
        y0 = mufin + sefin, y1 = mufin - sefin,
         code = 3, length = 0.05, angle = 90, lwd = 2,
        col = c(rgb(.4, .4, .4),
                rgb(.4, .4, .4),
                rgb(.4, .4, .4),
                rgb(1, 1, 1),
                rgb(.4, .4, .4),
                rgb(.4, .4, .4),
                rgb(.4, .4, .4),
                rgb(1, 1, 1)))


# Add points for populations 
points(x = c(0.25, 0.25, 0.25, 0.25),
       y = mgrowth_Control_in_Control-Control_in_Na$mean_growth,
       col = rgb(0, 0, 0, 0.05), bg = j.blue_alpha, pch = 21, cex = 1)
points(x = c(1.75, 1.75, 1.75, 1.75),
       y = mgrowth_Control_in_Control-Control_in_Temp$mean_growth,
       col = rgb(0, 0, 0, 0.05), bg = j.blue_alpha, pch = 21, cex = 1)
points(x = c(3.25, 3.25, 3.25, 3.25),
       y = mgrowth_Control_in_Control-Control_in_NaTemp$mean_growth,
       col = rgb(0, 0, 0, 0.05), bg = j.blue_alpha, pch = 21, cex = 1)

points(x = c(7.75, 7.75, 7.75, 7.75),
       y = mgrowth_Control_in_Control-Control_in_Na$mean_growth,
       col = rgb(0, 0, 0, 0.05), bg = j.blue_alpha, pch = 21, cex = 1)
points(x = c(9.25, 9.25, 9.25, 9.25),
       y = mgrowth_Control_in_Control-Control_in_Temp$mean_growth,
       col = rgb(0, 0, 0, 0.05), bg = j.blue_alpha, pch = 21, cex = 1)
points(x = c(10.75, 10.75, 10.75),
       y = mgrowth_Control_in_Control-NaTemp_in_NaTemp$mean_growth,
       col = rgb(0, 0, 0, 0.05), bg = j.red_alpha, pch = 21, cex = 1)


####################### CuTemp####################### 

par(mar=c(6, 6, 4, 2)) # bottom, left, top, right

CuTemp.bar <- barplot(c(rawD_cu_on_c, 
                     rawD_temp_on_c, 
                     rawD_cutemp_on_c,
                     rawD_cu_on_c+rawD_temp_on_c,
                     rawD_cu_on_c, 
                     rawD_temp_on_c, 
                     rawD_cutemp_on_e,
                     rawD_cu_on_c+rawD_temp_on_c), 
                   las = 1, xlab = "", ylab = "", yaxt = "n",
                   names.arg = c("C", "T", "CT", "+",
                                 "C'", "T'", "CT'", "+'"), 
                   cex.names = 1.5, 
                   ylim = c(-0.05, 0.365),
                   col = c(j.blue,
                           j.blue,
                           j.blue,
                           rgb(0.9, 0.9, 0.9),
                           j.blue,
                           j.blue,
                           j.red,
                           rgb(0.9, 0.9, 0.9)),
                   border = "white",
                   space = c(0.5, 0.5, 0.5, 0.5, 
                             2.0, 0.5, 0.5, 0.5))

axis(side = 2, at = c(0.0, 0.15, 0.3), 
     labels = c("0%", "15%", "30%"),
     cex.axis=1.5, las=1, lwd=1, lwd.ticks = 1)

abline(h = 0, lty = 1, lwd = 1, col = rgb(0.35, 0.35, 0.35))

mufin <- c(rawD_cu_on_c, 
           rawD_temp_on_c, 
           rawD_cutemp_on_c,
           rawD_cu_on_c+rawD_temp_on_c,
           rawD_cu_on_c, 
           rawD_temp_on_c,
           rawD_cutemp_on_e,
           rawD_cu_on_c+rawD_temp_on_c)
sefin <- c(rawSE_cu_on_c, 
           rawSE_temp_on_c,
           rawSE_cutemp_on_c,
           0,
           rawSE_cu_on_c, 
           rawSE_temp_on_c, 
           rawSE_cutemp_on_e,
           0)
arrows( x0 = CuTemp.bar, x1 = CuTemp.bar, 
        y0 = mufin + sefin, y1 = mufin - sefin,
         code = 3, length = 0.05, angle = 90, lwd = 2,
        col = c(rgb(.4, .4, .4),
                rgb(.4, .4, .4),
                rgb(.4, .4, .4),
                rgb(1, 1, 1),
                rgb(.4, .4, .4),
                rgb(.4, .4, .4),
                rgb(.4, .4, .4),
                rgb(1, 1, 1)))


# Add points for populations 
points(x = c(0.25, 0.25, 0.25, 0.25),
       y = mgrowth_Control_in_Control-Control_in_Cu$mean_growth,
       col = rgb(0, 0, 0, 0.05), bg = j.blue_alpha, pch = 21, cex = 1)
points(x = c(1.75, 1.75, 1.75, 1.75),
       y = mgrowth_Control_in_Control-Control_in_Temp$mean_growth,
       col = rgb(0, 0, 0, 0.05), bg = j.blue_alpha, pch = 21, cex = 1)
points(x = c(3.25, 3.25, 3.25, 3.25),
       y = mgrowth_Control_in_Control-Control_in_CuTemp$mean_growth,
       col = rgb(0, 0, 0, 0.05), bg = j.blue_alpha, pch = 21, cex = 1)

points(x = c(7.75, 7.75, 7.75, 7.75),
       y = mgrowth_Control_in_Control-Control_in_Cu$mean_growth,
       col = rgb(0, 0, 0, 0.05), bg = j.blue_alpha, pch = 21, cex = 1)
points(x = c(9.25, 9.25, 9.25, 9.25),
       y = mgrowth_Control_in_Control-Control_in_Temp$mean_growth,
       col = rgb(0, 0, 0, 0.05), bg = j.blue_alpha, pch = 21, cex = 1)
points(x = c(10.75, 10.75, 10.75, 10.75),
       y = mgrowth_Control_in_Control-CuTemp_in_CuTemp$mean_growth,
       col = rgb(0, 0, 0, 0.05), bg = j.red_alpha, pch = 21, cex = 1)

####################### All####################### 

par(mar=c(8, 6, 2, 2)) # bottom, left, top, right


All.bar <- barplot(c(rawD_na_on_c, 
                     rawD_cu_on_c, 
                     rawD_temp_on_c,
                     rawD_all_on_c,
                     rawD_na_on_c+rawD_cu_on_c+rawD_temp_on_c,
                     rawD_na_on_c, 
                     rawD_cu_on_c, 
                     rawD_temp_on_c,
                     rawD_all_on_e,
                     rawD_na_on_c+rawD_cu_on_c+rawD_temp_on_c), 
                   las = 1, xlab = "", ylab = "", yaxt = "n",
                   names.arg = c("N", "C", "T", "NCT", "+",
                                 "S'", "C'", "T'", "SCT'", "+'"),
                   cex.names = 1.5, 
                   ylim = c(-0.05, 0.365),
                   col = c(j.blue,
                           j.blue,
                           j.blue,
                           j.blue,
                           rgb(0.9, 0.9, 0.9),
                           j.blue,
                           j.blue,
                           j.blue,
                           j.red,
                           rgb(0.9, 0.9, 0.9)),
                   border = "white",
                   space = c(0.3, 0.3, 0.3, 0.3, 0.3, 
                             2.3, 0.3, 0.3, 0.3, 0.3))


axis(side = 2, at = c(0.0, 0.15, 0.3), 
     labels = c("0%", "15%", "30%"),
     cex.axis=1.5, las=1, lwd=1, lwd.ticks = 1)

abline(h = 0, lty = 1, lwd = 1, col = rgb(0.35, 0.35, 0.35))

mufin <- c(rawD_na_on_c, 
           rawD_cu_on_c, 
           rawD_temp_on_c,
           rawD_all_on_c,
           rawD_na_on_c+rawD_cu_on_c+rawD_temp_on_c,
           rawD_na_on_c, 
           rawD_cu_on_c, 
           rawD_temp_on_c,
           rawD_all_on_e,
           rawD_na_on_c+rawD_cu_on_c+rawD_temp_on_c)
sefin <- c(rawSE_na_on_c, 
           rawSE_cu_on_c, 
           rawSE_temp_on_c,
           rawSE_all_on_c,
           0,
           rawSE_na_on_c, 
           rawSE_cu_on_c, 
           rawSE_temp_on_c,
           rawSE_all_on_e,
           0)
arrows( x0 = All.bar, x1 = All.bar, 
        y0 = mufin + sefin, y1 = mufin - sefin,
         code = 3, length = 0.05, angle = 90, lwd = 2,
        col = c(rgb(.4, .4, .4),
                rgb(.4, .4, .4),
                rgb(.4, .4, .4),
                rgb(.4, .4, .4),
                rgb(1, 1, 1),
                rgb(.4, .4, .4),
                rgb(.4, .4, .4),
                rgb(.4, .4, .4),
                rgb(.4, .4, .4),
                rgb(1, 1, 1)))


# Add points for populations 
points(x = c(0.1, 0.1, 0.1, 0.1),
       y = mgrowth_Control_in_Control-Control_in_Na$mean_growth,
       col = rgb(0, 0, 0, 0.05), bg = j.blue_alpha, pch = 21, cex = 0.75)
points(x = c(1.45, 1.45, 1.45, 1.45),
       y = mgrowth_Control_in_Control-Control_in_Cu$mean_growth,
       col = rgb(0, 0, 0, 0.05), bg = j.blue_alpha, pch = 21, cex = 0.75)
points(x = c(2.75, 2.75, 2.75, 2.75),
       y = mgrowth_Control_in_Control-Control_in_Temp$mean_growth,
       col = rgb(0, 0, 0, 0.05), bg = j.blue_alpha, pch = 21, cex = 0.75)
points(x = c(4.0, 4.0, 4.0, 4.0),
       y = mgrowth_Control_in_Control-Control_in_All$mean_growth,
       col = rgb(0, 0, 0, 0.05), bg = j.blue_alpha, pch = 21, cex = 0.75)

points(x = c(8.6, 8.6, 8.6, 8.6),
       y = mgrowth_Control_in_Control-Control_in_Na$mean_growth,
       col = rgb(0, 0, 0, 0.05), bg = j.blue_alpha, pch = 21, cex = 0.75)
points(x = c(9.95, 9.95, 9.95, 9.95),
       y = mgrowth_Control_in_Control-Control_in_Cu$mean_growth,
       col = rgb(0, 0, 0, 0.05), bg = j.blue_alpha, pch = 21, cex = 0.75)
points(x = c(11.25, 11.25, 11.25, 11.25),
       y = mgrowth_Control_in_Control-Control_in_Temp$mean_growth,
       col = rgb(0, 0, 0, 0.05), bg = j.blue_alpha, pch = 21, cex = 0.75)
points(x = c(12.5, 12.5, 12.5, 12.5),
       y = mgrowth_Control_in_Control-All_in_All$mean_growth,
       col = rgb(0, 0, 0, 0.05), bg = j.red_alpha, pch = 21, cex = 0.75)

####################### Hedges g ############################

par(mar=c(4, 12, 4, 6)) # bottom, left, top, right

col_factor <- c(j.blue, j.red)[growth_trend_data$treatment_F]

plot(effect1 ~ treatment_J, data=growth_trend_data,
     las = 1, bty = "L", xaxt ="n", 
     ylim = c(-7.5, 2), xlim = c(-0.25, 1.9),
     cex=0, cex.axis=2.2, family = "Times",
     xlab = "", ylab = "")

abline(h = 0, lty = 1, lwd = 8, col = rgb(0, 0, 0, 0.1))

segments(x0 = c(growth_trend_data$treatment_J[1], 
                growth_trend_data$treatment_J[2], 
                growth_trend_data$treatment_J[3], 
                growth_trend_data$treatment_J[4]),
         y0 = c(growth_trend_data$effect2[1], 
                growth_trend_data$effect2[2], 
                growth_trend_data$effect2[3], 
                growth_trend_data$effect2[4]),
         x1 = c(growth_trend_data$treatment_J[5], 
                growth_trend_data$treatment_J[6], 
                growth_trend_data$treatment_J[7], 
                growth_trend_data$treatment_J[8]),
         y1 = c(growth_trend_data$effect2[5], 
                growth_trend_data$effect2[6], 
                growth_trend_data$effect2[7], 
                growth_trend_data$effect2[8]),
         col= rgb(0.85, 0.85, 0.85), lwd = 4, lty = 2)


arrows( x0 = growth_trend_data$treatment_J, 
        x1 = growth_trend_data$treatment_J, 
        y0 = growth_trend_data$cilow2,
        y1 = growth_trend_data$cihigh2,
        col= col_factor,
        code = 3, length = 0.1, angle = 90, lwd = 3)

box(which = "plot", lty = 1, lwd = 1.5)

points(c(growth_trend_data$treatment_J[1], growth_trend_data$treatment_J[2], 
         growth_trend_data$treatment_J[3], growth_trend_data$treatment_J[4]),
       c(growth_trend_data$effect2[1], growth_trend_data$effect2[2], 
         growth_trend_data$effect2[3], growth_trend_data$effect2[4]),
       pch = 19, col = j.blue, cex=7)

points(c(growth_trend_data$treatment_J[5], growth_trend_data$treatment_J[6], 
         growth_trend_data$treatment_J[7], growth_trend_data$treatment_J[8]),
       c(growth_trend_data$effect2[5], growth_trend_data$effect2[6], 
         growth_trend_data$effect2[7], growth_trend_data$effect2[8]),
       pch = 19, col = j.red, cex=7)

text(growth_trend_data$effect2 ~ growth_trend_data$treatment_J, 
     labels=growth_trend_data$number, family = "Times", 
     cex = 1.5, col = rgb(0.3, 0.3, 0.3))


```

<br>

### Suplementary Fig 2 - No Data

<br>

### Suplementary Video 1 - All Stressors (4 axes)

Resources: 

- http://www.sthda.com/english/wiki/impressive-package-for-3d-and-4d-graph-r-software-and-data-visualization 
- https://www.r-graph-gallery.com/3-r-animated-cube.html 


```{r, echo=FALSE}
x.coords = c(rawD_na_on_c, 0, 0, rawD_na_on_e, 0, 0)
y.coords = c(0, rawD_cu_on_c, 0, 0, rawD_cu_on_e, 0)
z.coords = c(0, 0, rawD_temp_on_c, 0, 0, rawD_temp_on_e)

x.coords_2 = x.coords+0.0055
y.coords_2 = y.coords+0.0055
z.coords_2 = z.coords+0.0055

########### Points ###########

scatter3D(x = x.coords, y = y.coords, z = z.coords,
          colvar = NULL, 
          col = c(j.blue, j.blue, j.blue, 
                  j.red, j.red, j.red),
          pch = 19, 
          cex = 3.5,
          xlim = c(-0.025, 0.19),
          ylim = c(-0.025, 0.19),
          zlim = c(-0.025, 0.19),
          box=FALSE,
          xlab = "Effect of Salt",
          ylab = "Effect of Copper",
          zlab = "Effect of Temperature",
          ticktype = "detailed")


scatter3D(x = c(coord_all_con, coord_all_evo, 
                coord_all_con_add, coord_all_evo_add),
          y = c(coord_all_con, coord_all_evo, 
                coord_all_con_add, coord_all_evo_add),
          z = c(coord_all_con, coord_all_evo, 
                coord_all_con_add, coord_all_evo_add),
          add = TRUE, 
          pch = 19, 
          cex = 3.5,
          col = c(j.blue, j.red, 
                  rgb(230/255, 240/255, 255/255), rgb(1, 0.9, 0.9)),
          colvar = NULL)


scatter3D(0, 0, 0,
          add = TRUE,
          pch = 8, 
          cex = 1, 
          col = rgb(0.25, 0.25, 0.25, alpha = 0.7))


########### Axis ############


segments3D(x0 = c(-0.02, 0, 0, -0.02),
        x1 = c(0.19, 0, 0, 0.19),
        y0 = c(0, -0.02, 0, -0.02),
        y1 = c(0, 0.19, 0, 0.19),
        z0 = c(0, 0, -0.02, -0.02),
        z1 = c(0, 0, 0.19, 0.19),
        add = TRUE)


############ Text ##############

text3D(x = c(coord_all_con+0.0065, coord_all_evo+0.0065, 
             coord_all_con_add+0.0055, coord_all_evo_add+0.0055),
       y = c(coord_all_con+0.0065, coord_all_evo+0.0065, 
             coord_all_con_add+0.0055, coord_all_evo_add+0.0055),
       z = c(coord_all_con+0.0065, coord_all_evo+0.0065, 
             coord_all_con_add+0.0055, coord_all_evo_add+0.0055),
       labels = c("SCT", "SCT'", "+", "+'"),
       add = TRUE, 
       colkey = FALSE, 
       cex = 1)

text3D(x = x.coords_2, y = y.coords_2, z = z.coords_2,
       labels = c("S", "C", "T", "S'", "C'", "T'"),
       add = TRUE, 
       colkey = FALSE, 
       cex = 1)

text3D(x = c(coord_all_con+0.01, coord_all_evo+0.01),
       y = c(coord_all_con, coord_all_evo), 
       z = c(coord_all_con-0.01, coord_all_evo-0.01),
       labels = c("Antagonistic", "Synergistic"),
       add = TRUE, 
       colkey = FALSE, 
       col = c(j.blue, j.red),
       cex = 1.25)

text3D(0.06, 0.12, 0.12, 
       labels = "Effect of All",
       add = TRUE, 
       colkey = FALSE, 
       col = rgb(0.65, 0.65, 0.65, 1),
       cex = 1)

######### Arrows ##############

arrows3D(x0 = rawD_na_on_c,
        x1 = rawD_na_on_e,
        y0 = 0.01, 
        y1 = 0.01,
        z0 = 0,
        z1 = 0,
        add = TRUE, type = "cone",
        col = j.red, lwd = 3, length = 0.1)

arrows3D(x0 = 0.01,
        x1 = 0.01,
        y0 = rawD_cu_on_c, 
        y1 = rawD_cu_on_e,
        z0 = 0,
        z1 = 0,
        add = TRUE, type = "cone",
        col = j.red, lwd = 3, length = 0.1)

arrows3D(x0 = 0.01,
        x1 = 0.01,
        y0 = 0.01, 
        y1 = 0.01,
        z0 = rawD_temp_on_c,
        z1 = rawD_temp_on_e,
        add = TRUE, type = "cone",
        col = j.red, lwd = 3, length = 0.1)

arrows3D(x0 = coord_all_con+0.01,
        x1 = coord_all_evo+0.01,
        y0 = coord_all_con+0.01,
        y1 = coord_all_evo+0.01,
        z0 = coord_all_con,
        z1 = coord_all_evo,
        add = TRUE, type = "cone",
        col = j.red, lwd = 3, length = 0.1)




########  Plot and then play/spin as RGL ###########

plotrgl(alpha=0.75, windowRect = c(0, 0, 1000, 1000),
        zoom = 1.5, smooth = TRUE) 

axes3d(c('x', 'y', 'z'),
       lwd=0.5,
       col=rgb(0.65, 0.65, 0.65),
       nticks = 3)

title3d(xlab = "Effect of Salt",
        ylab = "Effect of Copper",
        zlab = "Effect of Temperature",
        col=rgb(0.65, 0.65, 0.65))


#play3d( spin3d( axis = c(0, 0, 1), rpm = 2), duration = 30)


####### Save as gif ##########

#movie3d(
#  movie="3_Stressors", 
#  spin3d( axis = c(0, 0, 1), rpm = 2),
#  type = "gif", 
#  duration = 30, 
#  dir = "gif",
#  clean = T)

```




### Suplementary Video 2 - 3D perforamnce space

#### Part a


```{r, echo=FALSE}

########### Points ###########

## ALl ##
scatter3D(x = ad_all_to_na-All_CuTemp_removed,
          y = ad_all_to_cu-All_NaTemp_removed, 
          z = ad_all_to_temp-All_NaCu_removed,
          colvar = NULL, 
          col = j.red,
          pch = 19, 
          cex = 3.5,
          xlim = c(-0.1, 0.3),
          ylim = c(-0.1, 0.3),
          zlim = c(-0.1, 0.3),
          box=FALSE,
          ticktype = "detailed")

## NaCu ##
scatter3D(x = ad_nacu_to_na-NaCu_Cu_removed,
          y = ad_nacu_to_cu-NaCu_Na_removed, 
          z = ad_nacu_to_temp-NaCu_NaCu_removed,
          colvar = NULL, 
          col = j.red,
          pch = 19, 
          cex = 3.5,
          xlim = c(0, 0.3),
          ylim = c(0, 0.3),
          zlim = c(0, 0.3),
          box=FALSE,
          ticktype = "detailed",
          add = T)

## NaTemp ##
scatter3D(x = ad_natemp_to_na-NaTemp_Temp_removed,
          y = ad_natemp_to_cu-NaTemp_NaTemp_removed, 
          z = ad_natemp_to_temp-NaTemp_Na_removed,
          colvar = NULL, 
          col = j.red,
          pch = 19, 
          cex = 3.5,
          xlim = c(0, 0.3),
          ylim = c(0, 0.3),
          zlim = c(0, 0.3),
          box=FALSE,
          ticktype = "detailed",
          add = T)

## CuTemp ##
scatter3D(x = ad_cutemp_to_na-CuTemp_CuTemp_removed,
          y = ad_cutemp_to_cu-CuTemp_Temp_removed, 
          z = ad_cutemp_to_temp-CuTemp_Cu_removed,
          colvar = NULL, 
          col = j.red,
          pch = 19, 
          cex = 3.5,
          xlim = c(-0.05, 0.3),
          ylim = c(-0.05, 0.3),
          zlim = c(-0.05, 0.3),
          box=FALSE,
          ticktype = "detailed",
          add = T)

## Na ##
scatter3D(x = ad_na_to_na,
          y = ad_na_to_cu-Na_removed, 
          z = ad_na_to_temp-Na_removed,
          colvar = NULL, 
          col = j.red,
          pch = 19, 
          cex = 3.5,
          xlim = c(-0.05, 0.3),
          ylim = c(-0.05, 0.3),
          zlim = c(-0.05, 0.3),
          box=FALSE,
          ticktype = "detailed",
          add = T)

## Cu ##
scatter3D(x = ad_cu_to_na-Cu_removed,
          y = ad_cu_to_cu, 
          z = ad_cu_to_temp-Cu_removed,
          colvar = NULL, 
          col = j.red,
          pch = 19, 
          cex = 3.5,
          xlim = c(-0.05, 0.3),
          ylim = c(-0.05, 0.3),
          zlim = c(-0.05, 0.3),
          box=FALSE,
          ticktype = "detailed",
          add = T)

## Temp ##
scatter3D(x = ad_temp_to_na-Temp_removed,
          y = ad_temp_to_cu-Temp_removed, 
          z = ad_temp_to_temp,
          colvar = NULL, 
          col = j.red,
          pch = 19, 
          cex = 3.5,
          xlim = c(-0.05, 0.3),
          ylim = c(-0.05, 0.3),
          zlim = c(-0.05, 0.3),
          box=FALSE,
          ticktype = "detailed",
          add = T)

## Control ##
scatter3D(x = 0,
          y = 0, 
          z = 0,
          colvar = NULL, 
          col = j.blue,
          pch = 19, 
          cex = 3.5,
          xlim = c(-0.05, 0.3),
          ylim = c(-0.05, 0.3),
          zlim = c(-0.05, 0.3),
          box=FALSE,
          ticktype = "detailed",
          add = T)

########### Box ############

segments3D(x0 = c(0, 0, 0),
        x1 = c(0.25, 0, 0),
        y0 = c(0, 0, 0),
        y1 = c(0, 0.25, 0),
        z0 = c(0, 0, 0),
        z1 = c(0, 0, 0.25),
        add = TRUE)

#segments3D(x0 = c(0.25, 0.25, 0.25),
#        x1 = c(0.25, 0.25, 0),
#        y0 = c(0.25, 0.25, 0.25),
#        y1 = c(0, 0.25, 0.25),
#        z0 = c(0.25, 0.25, 0.25),
#        z1 = c(0.25, 0, 0.25),
#        add = TRUE)

#segments3D(x0 = c(0.25, 0.25, 0.25),
#        x1 = c(0.25, 0.25, 0),
#        y0 = c(0, 0, 0),
#        y1 = c(0.25, 0, 0),
#        z0 = c(0, 0, 0.25),
#        z1 = c(0, 0.25, 0.25),
#        add = TRUE)

#segments3D(x0 = c(0, 0, 0, 0),
#        x1 = c(0, 0, 0.25, 0.25),
#        y0 = c(0.25, 0.25, 0, 0.25),
#        y1 = c(0.25, 0, 0, 0.25),
#        z0 = c(0, 0.25, 0.25, 0),
#        z1 = c(0.25, 0.25, 0.25, 0),
#        add = TRUE)


############ Text ##############

text3D(x = ad_all_to_na-All_CuTemp_removed+0.0065,
       y = ad_all_to_cu-All_NaTemp_removed+0.0065, 
       z = ad_all_to_temp-All_NaCu_removed+0.0065,
       labels = c("SCT", "SCT", "SCT", "SCT"),
       add = TRUE, 
       colkey = FALSE, 
       cex = 0.7, 
       col = c(rgb(0.5, 0.5, 0.5)))

text3D(x = ad_nacu_to_na-NaCu_Cu_removed+0.0065,
       y = ad_nacu_to_cu-NaCu_Na_removed+0.0065, 
       z = ad_nacu_to_temp-NaCu_NaCu_removed+0.0065,
       labels = c("SC", "SC", "SC"),
       add = TRUE, 
       colkey = FALSE, 
       cex = 0.7, 
       col = c(rgb(0.5, 0.5, 0.5)))

text3D(x = ad_natemp_to_na-NaTemp_Temp_removed+0.0065,
       y = ad_natemp_to_cu-NaTemp_NaTemp_removed+0.0065, 
       z = ad_natemp_to_temp-NaTemp_Na_removed+0.0065,
       labels = c("ST", "ST", "ST"),
       add = TRUE, 
       colkey = FALSE, 
       cex = 0.7, 
       col = c(rgb(0.5, 0.5, 0.5)))

text3D(x = ad_cutemp_to_na-CuTemp_CuTemp_removed+0.0065,
       y = ad_cutemp_to_cu-CuTemp_Temp_removed+0.0065, 
       z = ad_cutemp_to_temp-CuTemp_Cu_removed+0.0065,
       labels = c("CT", "CT", "CT", "CT"),
       add = TRUE, 
       colkey = FALSE, 
       cex = 0.7, 
       col = c(rgb(0.5, 0.5, 0.5)))

text3D(x = ad_na_to_na+0.0065,
       y = ad_na_to_cu-Na_removed+0.0065, 
       z = ad_na_to_temp-Na_removed+0.0065,
       labels = c("S", "S", "S", "S"),
       add = TRUE, 
       colkey = FALSE, 
       cex = 0.7, 
       col = c(rgb(0.5, 0.5, 0.5)))


text3D(x = ad_cu_to_na-Cu_removed+0.0065,
       y = ad_cu_to_cu+0.0065, 
       z = ad_cu_to_temp-Cu_removed+0.0065,
       labels = c("C", "C", "C"),
       add = TRUE, 
       colkey = FALSE, 
       cex = 0.7, 
       col = c(rgb(0.5, 0.5, 0.5)))


text3D(x = ad_temp_to_na-Temp_removed+0.0065,
       y = ad_temp_to_cu-Temp_removed+0.0065, 
       z = ad_temp_to_temp+0.0065,
       labels = c("T", "T", "T", "T"),
       add = TRUE, 
       colkey = FALSE, 
       cex = 0.7, 
       col = c(rgb(0.5, 0.5, 0.5)))

text3D(x = 0+0.0065,
       y = 0+0.0065, 
       z = 0+0.0065,
       labels = "Con",
       add = TRUE, 
       colkey = FALSE, 
       cex = 0.7, 
       col = c(rgb(0.5, 0.5, 0.5)))


########  Plot and then play/spin as RGL ###########

plotrgl(alpha=0.75, windowRect = c(0, 0, 1000, 1000),
        zoom = 1.5, smooth = TRUE) 

### Axis ###
axes3d(c('x', 'y', 'z'),
       lwd=0.5,
       col=rgb(0.65, 0.65, 0.65),
       nticks = 6)

title3d(xlab = "Adaptation to Salt",
        ylab = "Adaptation to Copper",
        zlab = "Adaptation to Temperature",
        col=rgb(0.65, 0.65, 0.65))


# play / spin

#play3d( spin3d( axis = c(0, 0, 1), rpm = 2), duration = 30)


####### Save as gif ##########

#movie3d(
#  movie="3_Pareto_a", 
#  spin3d( axis = c(0, 0, 1), rpm = 2),
#  type = "gif", 
#  duration = 30, 
#  dir = "gif",
#  clean = T)


```

<br>

#### Part b

<br>

```{r, echo=FALSE}
x.coords = c(0, mean(ad_na_to_na), 0, 0)
y.coords = c(0, 0, mean(ad_cu_to_cu), 0)
z.coords = c(0, 0, 0, mean(ad_temp_to_temp))

x.coords_2 = x.coords+0.0055
y.coords_2 = y.coords+0.0055
z.coords_2 = z.coords+0.0055

########### Points ###########

scatter3D(x = x.coords, y = y.coords, z = z.coords,
          colvar = NULL, 
          col = c(j.blue, j.red, j.red, j.red),
          pch = 19, 
          cex = 3.5,
          xlim = c(0, 0.15),
          ylim = c(0, 0.15),
          zlim = c(0, 0.15),
          box=FALSE,
          ticktype = "detailed")

scatter3D(x = mean(ad_all_to_na)-All_CuTemp_removed,
          y = mean(ad_all_to_cu)-All_NaTemp_removed, 
          z = mean(ad_all_to_temp)-All_NaCu_removed,
          colvar = NULL, 
          col = j.red,
          pch = 19, 
          cex = 3.5,
          xlim = c(0, 0.15),
          ylim = c(0, 0.15),
          zlim = c(0, 0.15),
          box=FALSE, 
          ticktype = "detailed",
          add = T)

########### Box ############

segments3D(x0 = c(0, 0, 0),
        x1 = c(0.15, 0, 0),
        y0 = c(0, 0, 0),
        y1 = c(0, 0.15, 0),
        z0 = c(0, 0, 0),
        z1 = c(0, 0, 0.15),
        add = TRUE)

#segments3D(x0 = c(0.25, 0.25, 0.25),
#        x1 = c(0.25, 0.25, 0),
#        y0 = c(0.25, 0.25, 0.25),
#        y1 = c(0, 0.25, 0.25),
#        z0 = c(0.25, 0.25, 0.25),
#        z1 = c(0.25, 0, 0.25),
#        add = TRUE)

#segments3D(x0 = c(0.25, 0.25, 0.25),
#        x1 = c(0.25, 0.25, 0),
#        y0 = c(0, 0, 0),
#        y1 = c(0.25, 0, 0),
#        z0 = c(0, 0, 0.25),
#        z1 = c(0, 0.25, 0.25),
#        add = TRUE)

#segments3D(x0 = c(0, 0, 0, 0),
#        x1 = c(0, 0, 0.25, 0.25),
#        y0 = c(0.25, 0.25, 0, 0.25),
#        y1 = c(0.25, 0, 0, 0.25),
#        z0 = c(0, 0.25, 0.25, 0),
#        z1 = c(0.25, 0.25, 0.25, 0),
#        add = TRUE)


############ Text ##############

text3D(x = x.coords_2, y = y.coords_2, z = z.coords_2,
       labels = c("Con", "S", "C", "T"),
       add = TRUE, 
       colkey = FALSE, 
       cex = 1)

text3D(x = mean(ad_all_to_na)-All_CuTemp_removed+0.0065,
       y = mean(ad_all_to_cu)-All_NaTemp_removed+0.0065, 
       z = mean(ad_all_to_temp)-All_NaCu_removed+0.0065,
       labels = "SCT",
       add = TRUE, 
       colkey = FALSE, 
       cex = 1)

######### Arrows ##############

arrows3D(x0 = 0,
        x1 = mean(ad_na_to_na),
        y0 = 0, 
        y1 = 0,
        z0 = 0,
        z1 = 0,
        add = TRUE, type = "cone",
        col = j.red, lwd = 3, length = 0.1)

arrows3D(x0 = 0,
        x1 = 0,
        y0 = 0,
        y1 = mean(ad_cu_to_cu),
        z0 = 0,
        z1 = 0,
        add = TRUE, type = "cone",
        col = j.red, lwd = 3, length = 0.1)

arrows3D(x0 = 0,
        x1 = 0,
        y0 = 0, 
        y1 = 0,
        z0 = 0,
        z1 = mean(ad_temp_to_temp),
        add = TRUE, type = "cone",
        col = j.red, lwd = 3, length = 0.1)

arrows3D(x0 = 0,
        x1 = mean(ad_all_to_na)-All_CuTemp_removed,
        y0 = 0,
        y1 = mean(ad_all_to_cu)-All_NaTemp_removed,
        z0 = 0,
        z1 = mean(ad_all_to_temp)-All_NaCu_removed,
        add = TRUE, type = "cone",
        col = j.red, lwd = 3, length = 0.1)

########  Plot and then play/spin as RGL ###########

plotrgl(alpha=0.75, windowRect = c(0, 0, 1000, 1000),
        zoom = 1.5, smooth = TRUE) 

### Axis ###
axes3d(c('x', 'y', 'z'),
       lwd=0.5,
       col=rgb(0.65, 0.65, 0.65),
       nticks = 3)

title3d(xlab = "Adaptation to  Salt",
        ylab = "Adaptation to  Copper",
        zlab = "Adaptation to  Temperature",
        col=rgb(0.65, 0.65, 0.65))


# play / spin

#play3d( spin3d( axis = c(0, 0, 1), rpm = 2), duration = 30)


####### Save as gif ##########

#movie3d(
#  movie="3_Pareto_b", 
#  spin3d( axis = c(0, 0, 1), rpm = 2),
#  type = "gif", 
#  duration = 30, 
#  dir = "gif",
#  clean = T)
```
<br>
<br>